---
title: "word2vec like julia"
output: 
  html_document: 
    fig_height: 7
    fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I wanted to use Julia Silge her work to apply word 2 vec
on the huge podcast archive.

https://juliasilge.com/blog/word-vectors-take-two/

take a sample of the entire scraped/downloaded archive.

```{r}
library(tidytext)
library(tidyverse)
library(widyr) # you need the newest version 1.2
```

The datafile is a row per episode. 

```{r take sample}
sn_complete <- read_rds("df_sn.RDS")
dim(sn_complete)
format(object.size(sn_complete),units = "Mb")
set.seed(13455)
sn_sample <- sample_n(sn_complete, 200)
rm(sn_complete) # make some space
```

```{r}
slide_windows <- function(tbl, doc_var, window_size) {
    # each word gets a skipgram (window_size words) starting on the first
    # e.g. skipgram 1 starts on word 1, skipgram 2 starts on word 2
    
    each_total <- tbl %>% 
        group_by(!!doc_var) %>% 
        mutate(doc_total = n(),
               each_total = pmin(doc_total, window_size, na.rm = TRUE)) %>%
        pull(each_total)
    
    rle_each <- rle(each_total)
    counts <- rle_each[["lengths"]]
    counts[rle_each$values != window_size] <- 1
    
    # each word get a skipgram window, starting on the first
    # account for documents shorter than window
    id_counts <- rep(rle_each$values, counts)
    window_id <- rep(seq_along(id_counts), id_counts)

    
    # within each skipgram, there are window_size many offsets
    indexer <- (seq_along(rle_each[["values"]]) - 1) %>%
        map2(rle_each[["values"]] - 1,
             ~ seq.int(.x, .x + .y)) %>% 
        map2(counts, ~ rep(.x, .y)) %>%
        flatten_int() +
        window_id
    
    tbl[indexer, ] %>%
        bind_cols(data_frame(window_id)) %>%
        group_by(window_id) %>%
        filter(n_distinct(!!doc_var) == 1) %>%
        ungroup
}
```

First have to unpack the nested dataframe. 

```{r unpack into tidy pmi}

tidy_pmi <- sn_sample %>%
    unnest(text) %>% 
    unnest_tokens(word, text) %>%
    add_count(word) %>%
    filter(n >= 20) %>%
    select(-n) %>%
    slide_windows(quo(ep_nr), 8) %>%
    pairwise_pmi(word, window_id)

```


```{r tidy word vectors}
tidy_word_vectors <- tidy_pmi %>%
    widely_svd(item1, item2, pmi, nv = 256, maxit = 1000)
```

find nearest words

```{r}
nearest_synonyms <- function(df, token) {
    df %>%
        widely(~ . %*% (.[token, ]), sort = TRUE)(item1, dimension, value) %>%
        select(-item2)
}
```

Let's try to find some synonyms
```{r synonym finding, eval=FALSE}
tidy_word_vectors %>%
    nearest_synonyms("microsoft")
# in sample not: breach python, virus # ow it is
tidy_word_vectors %>%
    nearest_synonyms("apple")
tidy_word_vectors %>%
    nearest_synonyms("google")
tidy_word_vectors %>%
    nearest_synonyms("computer")  # not: bitcoin, crypto, crypocurrency
tidy_word_vectors %>%
    nearest_synonyms("safe") #
# secure, changing, encrypted, 
# bitcoin: cryptolocker, payment, worth, dollars, visa, price
# crypto: technology, cryptography, encryption, implementaiton, beautiful, symmetric
tidy_word_vectors %>%
    nearest_synonyms("program") # broken, fail, owned, open,program
# broken: badley, massive, anything, trouble, crypto, fbi, nsa
# open: pictures, financial, google, signal, has creating, skype  (being owned by someone)
tidy_word_vectors %>%
    nearest_synonyms("steve")
# steve: leo, yeah, i, you, it's, right, just, yes, yup (the way he talks)
tidy_word_vectors %>%
    nearest_synonyms("leo")
# leo: steve, yeah, i, you, right, oh, yes,
tidy_word_vectors %>%
    nearest_synonyms("gibson") # only used at start and finish
# mr chief explainer, steven, recored, corperation
tidy_word_vectors %>%
    nearest_synonyms("spinrite") # clearly often used with the 
# same sentences: spinrite drive, recovery, maintenance, drives, world's
# best disk 
#tidy_word_vectors %>%
#    nearest_synonyms("steve")
#tidy_word_vectors %>%
#    nearest_synonyms("hard")
tidy_word_vectors %>%
    nearest_synonyms("web")
tidy_word_vectors %>%
    nearest_synonyms("podcast")
#tidy_word_vectors %>%
#    nearest_synonyms("netcast")# does not exist
tidy_word_vectors %>%
    nearest_synonyms("guy") # he's, named, man, himself, chief, steven, he, him, who.
tidy_word_vectors %>%
    nearest_synonyms("guys") # researchers, these, people, presentation,microsoft, tools
#tidy_word_vectors %>%
#    nearest_synonyms("girl") # not in there
#tidy_word_vectors %>%
#    nearest_synonyms("woman") # not in there, neither women
tidy_word_vectors %>%
    nearest_synonyms("man")# middle, gibson, mr, chief, explainer, creator, corperation
# men does not exist
#tidy_word_vectors %>%
#    nearest_synonyms("female") # not in there
tidy_word_vectors %>%
    nearest_synonyms("male") # voice, male, jim, games, military, strategy, 
# basic, bet, young


tidy_word_vectors %>%
    nearest_synonyms("bad") # arbitrary, an, big, good, problem, sites, guys, news
tidy_word_vectors %>%
    nearest_synonyms("good") # great, security, had, yes, again, think
tidy_word_vectors %>%
    nearest_synonyms("he") # verbs: who, says, said, was, about
tidy_word_vectors %>%
    nearest_synonyms("she") # he, bob, sally, who, wife, where, client
tidy_word_vectors %>%
    nearest_synonyms("guy")
```




What are some analogies we can find in this podcast corpus? Let’s write a little function that will find the answer to token1 - token2 + token 3 = ???.
```{r}
analogy <- function(df, token1, token2, token3) {
    df %>%
        widely(~ . %*% (.[token1, ] - .[token2, ] + .[token3, ]), sort = TRUE)(item1, dimension, value) %>%
        select(-item2)
    
}
```

```{r finding analogies}
## operating systems
tidy_word_vectors %>%
    analogy("mac", "apple", "microsoft") # xp, vulnerabilities, pc
tidy_word_vectors %>%
    analogy("computer", "microsoft", "apple") #  apple, computer, ios, iphone
tidy_word_vectors %>%
    analogy("steve", "spinrite", "apple")
tidy_word_vectors %>%
    analogy("steve", "spinrite", "microsoft")
tidy_word_vectors %>%
    analogy("computer", "wifi", "bluetooth") # machine, off, existing, radio
tidy_word_vectors %>% analogy("pc", "screen", "computer")
# pc minus a screen, plus computer is virtual, vmware, workstation, server
```

```{r}
tidy_word_vectors %>%
    analogy("steve", "spinrite", "leo")
```



Since we have done a singular value decomposition, we can use our word vectors to understand what principal components explain the most variation in the Hacker News corpus.
```{r plot principle components}
tidy_word_vectors %>%
    filter(dimension <= 24) %>%
    group_by(dimension) %>%
    top_n(12, abs(value)) %>%
    ungroup %>%
    mutate(item1 = reorder(item1, value)) %>%
    group_by(dimension, item1) %>%
    arrange(desc(value)) %>%
    ungroup %>%
    mutate(item1 = factor(paste(item1, dimension, sep = "__"), 
                         levels = rev(paste(item1, dimension, sep = "__"))),
           dimension = factor(paste0("Dimension ", dimension),
                              levels = paste0("Dimension ", as.factor(1:24)))) %>%
    ggplot(aes(item1, value, fill = dimension)) +
    geom_col(show.legend = FALSE) +
    facet_wrap(~dimension, scales = "free_y", ncol = 4) +
    scale_x_discrete(labels = function(x) gsub("__.+$", "", x)) +
    coord_flip() +
    labs(x = NULL, y = "Value",
         title = "First 24 principal components of the security now corpus",
         subtitle = "Top words contributing to the components that explain the most variation")
         
```

First dimension describes general leo, yeah, steve, etc. 
dimension 3 seems to describe earlier episodes, dim4 describes end of podcast

13 is about network and routers. dim 16, encryption ssl, cipher, code attacker
dim 19 certificates. dim 22 surveillance and nation states


